Making Sequential Programs Deterministic

### 2019-03-26 design.tex
type validity section

The (determinism) type of a Collection or Iterator must be a supertype or equal to
the type of the type parameter (see Figure~\ref{fig-determinism-collections}).
If the Collection is \<NonDet>, then the type parameter may not be
\<Det> or \<OrderNonDet>. Although such types could exist, they are
disallowed to prevent the following bug:

@@

Similarly, the (determinism) type of an array must be a supertype or equal to
the type of the component type (see Figure~\ref{fig-determinism-collections}).
As with collections, \codeid{@NonDet} arrays of \codeid{@Det} or \codeid{@OrderNonDet}
elements are not allowed.

>>>>

Figure~\ref{type-validity} shows the type validity rules of our type system. A type $\tau$ is represented as $\kappa \ \beta$
where $\kappa$ is a type qualifier from the determinism type hierarchy and $\beta$ is a Java type.
As stated in the rule $\sc{\mathit{ANY\ TYPE}}$, the types \<Det> and \<NonDet> can be written on any Java type.
The (determinism) type of a Collection or Iterator must be a supertype or equal to
the type of the type parameter (Rule $\sc{\mathit{ORDERNONDET \ COLLECTION}}$) (see Figure~\ref{fig-determinism-collections}).
If the Collection is \<NonDet>, then the type parameter may not be
\<Det> or \<OrderNonDet> (Rule $\sc{\mathit{NONDET \ COLLECTION}}$ in Figure~\ref{type-validity}). Although such types could exist, they are
disallowed to prevent the following bug:

@@

Similarly, the (determinism) type of an array must be a supertype or equal to
the type of the component type (see Figure~\ref{fig-determinism-collections}).
As with collections, \codeid{@NonDet} arrays of \codeid{@Det} or \codeid{@OrderNonDet}
elements are not allowed (Rules $\sc{\mathit{ORDERNONDET \ ARRAY}}$ and $\sc{\mathit{NONDET \ ARRAY}}$ in Figure~\ref{type-validity}).
